paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the paper.qmd file

---
title: "paper"
author: "Chay Park"
date: 22 January 2024
format: pdf
editor: visual
---

```{r}
#### Preamble ####
# Purpose: Read in data from the Toronto Police Annual Report - Victims of Crimes and provide relevant tables and graphs of the dataset.
# Author: Chay Park
# Email: chay.park@mail.utoronto.ca
# Date: Jan 22, 2024
# Prerequisites: Need to know where to get Toronto Police Annual Report - Victims of Crimes
```

@@

```{r}
# Install the necessary packages if not already installed
# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse"))

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)

# Read CSV
unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")

# Filter out unknown values for SEX and rows with 'other' values for SUBTYPE
cleaned_data <- unedited_data %>%
  filter(SEX %in% c("M", "F") & AGE_GROUP != "Unknown" & SUBTYPE != "Other")

head(cleaned_data)
```

@@

```{r}
#### Table 1a ####
# Count the Child group victims, Youth group victims, Adult group victims over the year from 2014 to 2022
####  ####

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)

@@

# Print the table using knitr
kable(pivoted_table, format = "markdown", caption = "Total number of victims in different age group from 2014 to 2022")

@@

```{r}
#### Bar graph 1a ####
# Bar graph 1a illustrates the number of reported crimes in different age group over the year from 2014 to 2022. 
#### ####

@@

```{r}
# Load required libraries
library(dplyr)
library(ggplot2)

@@

```{r}
# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)

@@

# Print the table using knitr
kable(pivoted_table2, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")

@@

```{r}
# Load required libraries
library(dplyr)
library(ggplot2)

@@

### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.

Gelfand, Sharla. 2020. *Opendatatoronto : Access the City of Toronto Open Data Portal*

R Core Team. 2020. *R: A Language and Environment for Statistical Computing.* Vienna, Austria: R Foundation for Statistical Computing. https://www.R-project.org/.

Toronto Police Services. 2023. *TPS Police Annual Statistical Report - Victims of Crimes*

Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019. "Welcome to the tidyverse." *Journal of Open Source Software* 4 (43): 1686. https://doi.org/10.21105/joss.01686.

\
Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2021. *Dplyr: A Grammar of Data Manipulation.*https://CRAN.R-project.org/package=dplyr.

Xie, Yihui. 2014. "Knitr: A Comprehensive Tool for Reproducible Research in R." *In Implementing Reproducible Computational Research*, edited by Victoria Stodden, Friedrich Leisch, and Roger D. Peng. Chapman; Hall/CRC. http://www.crcpress.com/product/isbn/9781466561595.

>>>>

---
title: "paper"
author: "Chay Park"
date: today
format: pdf
editor: visual
bibliography: references.bib
---

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| include: false

#### Preamble ####
# Purpose: Read in data from the Toronto Police Annual Report - Victims of Crimes and provide relevant tables and graphs of the dataset.
# Author: Chay Park
# Email: chay.park@mail.utoronto.ca
# Date: Jan 22, 2024
# Prerequisites: Need to know where to get Toronto Police Annual Report - Victims of Crimes
```

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

#### Table 1a ####
# Count the Child group victims, Youth group victims, Adult group victims over the year from 2014 to 2022
####  ####

# Install the necessary packages if not already installed
install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(flextable)

# Load the csv file
cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))

@@

# Print the table
flextable(head(pivoted_table))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

#### Bar graph 1a ####
# Bar graph 1a illustrates the number of reported crimes in different age group over the year from 2014 to 2022. 
#### ####

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

# Load the csv file
cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(flextable)

# Load the csv file
cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))

@@

# Print the table
flextable(head(pivoted_table2))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

---
nocite: '@*'
---
